\textbf{Datasets:}

There are 58 relevant datasets in the HST archive intersecting the coordinates of MACSJ1149 that 
will be used in this work. The data are from the WFC3-IR and ACS-WFC instruments, and span 
April 22, 2004-October 30, 2016 with HST Project IDs: 9722,\ 10493,\ 12068,\ 12197,\ 13504,\
13459,\ 14041,\  13790,\ 14199, and 14208. NEED TO ADD HOW WE'RE GETTING THE DATA,
HOW LONG IT'LL TAKE, ETC.

\bigskip

\noindent\textbf{Analysis:}

First, as described in the scientific justification, previous photometry will be improved by using both
the \textit{PythonPhot} and \textit{DOLPHOT} packages, which will minimize potential systematic errors
in either method. In addition, foreground stars within the MACS11489 datasets described above
will be used to define a variable point spread function (PSF) model, which will account for known 
subtle variations due to telescope "breathing" (\textbf{CITE}).

For lensed SNe, it is possible to classify the SN based on photometry and spectroscopy, and then
identify a well-matched SN light curve template. In contrast to quasar time delay measurements that
use a flexible function fitting method, the template method provides a strong informative prior for the 
intrinsic light curve shape. In the case of SN Refsdal, the initial analysis concluded that a SN 1987A-like
template fits the data best \citep{Kelly:2015c}, and we will confirm this with our own new analytical 
software package being developed in this work. The SN 1987A template will be corrected to match the 
redshift of SN Refsdal, measured to be $z=1.488\pm.001$\citep{Rodney:2016}, and then a Bayesian
parameter estimation framework will be implemented to estimate the color corrections, time delays, and
magnifications for all four SN Refsdal images. Previously ignored microlensing effects will be considered
by analyzing achromatic deviations from the light curve templates in conjunction with a Bayesian prior 
that describes microlensing probability as a function of time. Microlensing effects identified by the model 
are corrected so that the inherent light curve can be compared to the template, and the correct template
parameters derived. The model light curves are defined using
\begin{equation}
m(\lambda',t')=M(\lambda,t)+K(\lambda,t;\lambda')+C_\lambda,
\end{equation}
where the time t is the rest-frame age relative to the date of peak brightness in the rest-frame R band, 
and is a free parameter in the model. The model apparent magnitude in an observed passband,
$m(\lambda',t')$, is governed by a model absolute magnitude in a model passband at the model's rest-
frame age, $M(\lambda,t)$, corrected to an observed passband with $K(\lambda,t;\lambda')$ 
\citep{Strolger:2015}. Finally, a magnitude shift $C_\lambda$ is added as a separate free parameter
for each photometric passband, which accounts for both cosmological dimming and any color difference
between the model and SN Refsdal due to dust extinction or intrinsic color differences. Linear interpolation
will be used to infer model magnitudes between observed points in the template light curves.

To take into account the gravitational lensing effects, we will include six more free parameters that are
applied as corrections to the observed data: time shifts $\delta t_i$, and achromatic magnitude
shifts $\delta m_i$ that give the time delays and magnifications of the the Refsdal sources relative to
a reference source. The model light curves are then simultaneously compared to all SN Refsdal sources
to derive a likelihood distribution from each light curve template $T_k$, using:
\begin{equation}
p(D|T_k,\theta)=\prod\limits_i\frac{p_i(\theta)}{\sqrt{2\pi}\sigma_i}e^{-(m_{obs(t_i)}-m_k(\lambda_i,t_i))^2
/(2\sigma^2_i)}.
\end{equation}
Here $\theta$ denotes the set of free parameters, and $p_i(\theta)$ are the Bayesian prior distributions. 
In contrast with previous analysis done on SN Refsdal, a microlensing parameter will be added to the set 
$\theta$, and the related Bayesian prior distribution will not be flat. In order to sample the likelihood distributions 
defined by Equation (2) over the multidimensional parameter space, we will use the Markov Chain Monte Carlo
ensemble sampling tools from the \textit{SNCosmo} software package \citep{Barbary:2014}.


%\begin{tabular}{ccccc}
%\centering
%Start Date & Start MJD &Total Integration Time (s)&Instrument & HST Program ID\\
%\hline
%\hline
%2004 Apr 22.6&53117.6&63630&ACS&9722\\
%2006 May 25.5&53880.5&15288&ACS&10493\\
%2010 Dec 04.9&55534.9&14462&ACS&12068\\
%2010 Dec 05.0&55535.0&10058.7&WFC3&12068\\
%2011 Jan 16.0&55577.0&14532&ACS&12068\\
%2011 Jan 16.0&55577.0&10058.7&WFC3&12068\\
%2011 Jan 30.6&55591.6&14462&ACS&12068\\
%2011 Jan 30.7&55591.7&10058.7&WFC3&12068\\
%2011 Feb 13.3&55605.3&14329&ACS&12068\\
%2011 Feb 13.3&55605.3&64691&WFC3&12068\\
%2011 Feb 27.0&55619.0&14182&ACS&12068\\
%2011 Feb 27.1&55619.1&9758.7&WFC3&12068\\
%2011 Feb 27.5&55619.5&13916&ACS&12068\\
%2011 Feb 27.6&55619.6&28386.8&WFC3&12068\\
%2011 Mar 09.8&55629.8&14595&ACS&12068\\
%2011 Mar 09.8&55629.8&10058.67676&WFC3&12068\\
%2012 Feb 07.9&55964.9&22387.7&WFC3&12197\\
%2013 Nov 02.2&56598.2&20632.9&WFC3&13504\\
%2013 Nov 12.8&56608.8&309120&WFC3&13389\\
%2014 Feb 23.4&56711.4&71728.7&WFC3&13459\\
%2014 Apr 14.7&56761.7&36722&ACS&13504\\
%2014 Nov 03.1&56964.1&51234.8&WFC3&13459\\
%2014 Nov 11.0&56972.0&20693.9&WFC3&13459\\
%2014 Nov 20.0&56981.0&20847&WFC3&13504\\
%2014 Nov 20.8&56981.8&190423&WFC3&13504\\
%2014 Nov 24.1&56985.1&65170&WFC3&14041\\
%2014 Nov 29.9&56990.9&55623&WFC3&13790\\
%2014 Dec 11.8&57002.8&154329&WFC3&13504\\
%2014 Dec 22.9&57013.9&74312&WFC3&13790\\
%2014 Dec 23.7&57014.7&10232&WFC3&14041\\
%2014 Dec 23.8&57014.8&88988&WFC3&13504\\
%2014 Dec 25.6&57016.6&51161&WFC3&14041\\
%2014 Dec 26.7&57017.7&44494&WFC3&13504\\
%2014 Dec 27.6&57018.6&92091&WFC3&14041\\
%2014 Dec 29.5&57020.5&44494&WFC3&13504\\
%2014 Dec 29.7&57020.7&71626&WFC3&14041\\
%2015 Jan 01.7&57023.7&44494&WFC3&13504\\
%2015 Jan 02.7&57024.7&20465&WFC3&14041\\
%2015 Jan 03.4&57025.4&44494&WFC3&13504\\
%2015 Jan 03.7&57025.7&40929&WFC3&14041\\
%2015 Jan 04.4&57026.4&44494&WFC3&13504\\
%2015 Jan 04.8&57026.8&20465&WFC3&14041\\
%2015 Jan 05.7&57027.7&65341&WFC3&13504\\
%2015 Jan 11.9&57033.9&86234&WFC3&13790\\
%2015 Apr 19.4&57131.4&68068&ACS&13504\\
%2015 Apr 20.1&57132.1&9106&WFC3&13790\\
%2015 Apr 20.5&57132.5&748076&ACS&13504\\
%2015 May 07.0&57149.0&9106&WFC3&13790\\
%2015 May 07.4&57149.4&314090&ACS&13504\\
%2015 May 26.3&57168.3&57999&WFC3&13790\\
%2015 Oct 30.8&57325.8&144163&WFC3&14199\\
%2016 May 16.3&57524.3&32850&WFC3&14208\\
%2016 May 16.5&57524.5&28964&WFC3&14199\\
%2016 May 23.3&57531.3&9896&WFC3&14208\\
%2016 May 23.4&57531.4&14604&ACS&14208\\
%2016 May 24.0&57532.0&183128&WFC3&14199\\
%2016 Oct 30.2&57691.2&&9670&WFC3&14199\\
%\end{tabular} 
%


